Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-21 papers/ms.tex
update ms

\newcommand{\npms}{1097} % 20220311_Kerr_SPYGLASS205_Members_All.csv

@@

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric, defined
such that the group member with the smallest core distance has a
weight of 1, the group member with the greatest core distance has a
weight of 0, and weights for the other group members are log-normally
distributed between these two extremes.  In Figure~\ref{fig:XYZvtang},
we show 12{,}436 objects with weight exceeding 0.02 as gray points,
and overplot 4{,}763 objects with weights exceeding 0.10 as black
points ({\bf @LGB: slightly more description of the ``weight'' parameter
is needed}).\footnote{These counts only include objects with reliable
astrometry and photometry: $\varpi/\sigma_\varpi>5$;
$G/\sigma_{G}>50$; $G_{\rm RP}/\sigma_{G_{RP}}>20$; $G_{\rm
BP}/\sigma_{G_{BP}}>20$.} The previously known $\delta$~Lyr\ cluster
is visible at $(l,b)=(68^\circ,15^\circ$) and $(v_{l'}, v_b)=(-4.5
,-4 )\mkms$.  RSG-5 is visible at $(l,b)=(83^\circ,6^\circ)$,
$(v_{l'}, v_b)=(5.5 ,-3.5 )\mkms$.  Most of the other
subclusters, including in Cep-Cyg ($l,b=90^\circ,7^\circ$) and
Cerberus ($l,b=48^\circ,18^\circ$) are too small or dispersed to have
previously been analyzed in great detail.

>>>>

\newcommand{\npms}{1{,}097} % 20220311_Kerr_SPYGLASS205_Members_All.csv

@@

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric,
$\alpha$, defined such that the group member with the smallest core
distance has $\alpha=1$, the group member with the greatest core
distance has $\alpha=0$, and weights for the other group members are
log-normally distributed between these two extremes.  After applying a
set of quality cuts on the astrometry and
photometry,\footnote{$\varpi/\sigma_\varpi>5$; $G/\sigma_{G}>50$;
$G_{\rm RP}/\sigma_{G_{RP}}>20$; $G_{\rm BP}/\sigma_{G_{BP}}>20$.}
this procedure yields $\alpha \sim \log_{10}\mathcal{N}(-1.55,0.61)$.
To visualize the results, in Figure~\ref{fig:XYZvtang} we show
12{,}436 objects with weight exceeding 0.02 as gray points, and
overplot 4{,}763 objects with weights exceeding 0.10 as black points.
The previously known $\delta$~Lyr\ cluster is visible at
$(l,b)=(68^\circ,15^\circ$) and $(v_{l'}, v_b)=(-4.5 ,-4 )\mkms$.
RSG-5 is visible at $(l,b)=(83^\circ,6^\circ)$, $(v_{l'}, v_b)=(5.5
,-3.5 )\mkms$.  Most of the other subclusters, including in Cep-Cyg
($l,b=90^\circ,7^\circ$) and Cerberus ($l,b=48^\circ,18^\circ$) are
too small or dispersed to have previously been analyzed in great
detail.
